%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EPFL report package, main thesis file
% Goal: provide formatting for theses and project reports
% Author: Mathias Payer <mathias.payer@epfl.ch>
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[a4paper,12pt,oneside]{report}
% Options: MScThesis, BScThesis, MScProject, BScProject
\usepackage[BScThesis]{EPFLreport}
\usepackage{xspace}
\usepackage{notoccite}

\title{Rotation estimation of detected satellites}
\author{Noah Kaltenrieder (301368)}
\supervisor{Mathieu Salzmann}
%\adviser{Prof. Dr. sc. ETH Mathias Payer}
%\coadviser{Second Adviser}
%\expert{The External Reviewer}

\newcommand{\sysname}{FooSystem\xspace}

\begin{document}
\maketitle
%\makededication
\acknowledgments{
    I really would like to thank my supervisor Prof. Mathieu Salzmann who helped me a lot and all the people that participated
    in a way to this project, namely Dr. Cameron Lemon, Prof. Jean-Paul Kneib, Prof. Frédéric Courbin, and the SSA Team. I also want to express
    my gratitude to Yann Bouquet who helped me with pleasure when I had questions. Finally, I also would like to especially thank 
    Alexandre Di Piazza and Marcellin Feasson with whom I have collaborated through all the semester in different ways.
    \newline 
    Thanks a lot to Prof. Mathias Payer for the thesis template that I used to write this report~\cite{templateRef}
}
\makeacks

\begin{abstract}
I present an approach to extract the intensity along the satellite streaks that can be found in images that were obtained by OMEGACAM 
on the VLT Survey Telescope. In this project, I only analyzed the long tracks that were created by high velocity objects, to
try to get an estimation about their rotation. I used Fourier transform to get the periodicity of the intensity along the tracks.
Due to the lack of real data about rotation, I first had to create fake streaks with sinusoid intensity and different angles.
I manually get the tracks to run my code on them, so ideally this project should be integrated with DetectSat~\cite{detectsatRepo} so that all 
the process can be done automatically. I found very great result with it and run the pipeline on real tracks. By making assumptions about the satellite, 
like their altitude, I get possible results, but since we don't have access to the real values, we can't say if it is close to reality or not.
\end{abstract}

%\begin{frenchabstract}
%For a doctoral thesis, you have to provide a French translation of the
%English abstract. For other projects this is optional.
%\end{frenchabstract}

\maketoc

%%%%%%%%%%%%%%%%%%%%%%
\chapter{Introduction}
%%%%%%%%%%%%%%%%%%%%%%

This project is about estimating the rotation of spatial objects detected by the OMEGACAM on the VLT Survey Telescope. In these times,
we have a lot of flying objects, it can be debris, useful satellites or dead satellites, around the Earth and it becomes more and more
necessary to have a clear view of all these objects.
The project of Yann Bouquet "DetectSat"\cite{detectsatRepo} was focused on detection of the satellite tracks on fits files, but with both,
small (low velocity) and long (high velocity) streaks. To this project I had to focus on the long tracks, so that the variation of intensity
along the line could be better detected. The rotation estimation can be used to determine which kind of object the streak is and, if it is
a satellite, it may be used to better find out which one it is. Ideally, this should be run on the lines detected by DetectSat so all the process
could be done with only the fits file as input.
\newline
\newline
The main challenge is that we don't have access to data about rotation of satellites, so I had to first create my own streaks 
with sinusoid intensity. This lack of resources is very restrictive, since even if I get a result, we cannot know the precision of this method 
and we cannot be sure that it is right or completely wrong. This is why I had to begin with creating lines that seem realistic and
try with random angles.
\newline
\newline
The second part of this project was to retrieve the periodicity of the sinusoidal function along the streaks that I generated, and finally
try this on real tracks. Since my project does not recognize the lines, I had to find the coordinates of the streaks by hand and give them
as input to the pipeline. For this part, there are many factors that can decrease the precision of the pipeline, e.g., if the line crosses a
really bright star, it gives a peak of intensity and can lead to wrong result, or if the brightness of the streak is too small
compared to the brightness of the background of the sky on the image. 




The introduction is a longer writeup that gently eases the reader into your
thesis~\cite{dinesh20oakland}. Use the first paragraph to discuss the setting.
In the second paragraph you can introduce the main challenge that you see.
The third paragraph lists why related work is insufficient.
The fourth and fifth paragraphs discuss your approach and why it is needed.
The sixth paragraph will introduce your thesis statement. Think how you can
distill the essence of your thesis into a single sentence.
The seventh paragraph will highlight some of your results
The eights paragraph discusses your core contribution.

This section is usually 3-5 pages.

%%%%%%%%%%%%%%%%%%%%
\chapter{Background}
%%%%%%%%%%%%%%%%%%%%

The background section introduces the necessary background to understand your
work. This is not necessarily related work but technologies and dependencies
that must be resolved to understand your design and implementation.

This section is usually 3-5 pages.


%%%%%%%%%%%%%%%%
\chapter{Design}
%%%%%%%%%%%%%%%%

Introduce and discuss the design decisions that you made during this project.
Highlight why individual decisions are important and/or necessary. Discuss
how the design fits together.

This section is usually 5-10 pages.


%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Implementation}
%%%%%%%%%%%%%%%%%%%%%%%%

The implementation covers some of the implementation details of your project.
This is not intended to be a low level description of every line of code that
you wrote but covers the implementation aspects of the projects.

This section is usually 3-5 pages.


%%%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}
%%%%%%%%%%%%%%%%%%%%

In the evaluation you convince the reader that your design works as intended.
Describe the evaluation setup, the designed experiments, and how the
experiments showcase the individual points you want to prove.

This section is usually 5-10 pages.


%%%%%%%%%%%%%%%%%%%%%%
\chapter{Related Work}
%%%%%%%%%%%%%%%%%%%%%%

The related work section covers closely related work. Here you can highlight
the related work, how it solved the problem, and why it solved a different
problem. Do not play down the importance of related work, all of these
systems have been published and evaluated! Say what is different and how
you overcome some of the weaknesses of related work by discussing the 
trade-offs. Stay positive!

This section is usually 3-5 pages.


%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion}
%%%%%%%%%%%%%%%%%%%%

In the conclusion you repeat the main result and finalize the discussion of
your project. Mention the core results and why as well as how your system
advances the status quo.

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\printbibliography

% Appendices are optional
% \appendix
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \chapter{How to make a transmogrifier}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% In case you ever need an (optional) appendix.
%
% You need the following items:
% \begin{itemize}
% \item A box
% \item Crayons
% \item A self-aware 5-year old
% \end{itemize}

\end{document}